Systematic Testing with Data-Race Preemption Points

### 2015-09-21 pldi-16/paper.tex
write more pldi

\title{Systematic Testing with Data-Race Preemption Points}
\authorinfo{Ben Blum}{Carnegie Mellon University}{bblum@cs.cmu.edu}
\authorinfo{Garth Gibson}{Carnegie Mellon University}{garth@cs.cmu.edu}

@@

% Can I even make a claim this broad to begin with?
However, all stateless model checkers to date are bound by a fixed set of {\em preemption points} (PPs): code locations that define the granularity at which threads interleave.
For example, CHESS \cite{chess} preemptions only on synchronization operations and library calls, which can miss lock-free shared memory races.
It provides an additional data-race analysis to report any violations of this model;
% TODO: Make sure that there are enough citations for this claim.
however, data-race analyses are prone to report false positives and benign races which require annotations or imprecise heuristics to reduce \cite{racerx,tsan,datacollider}.
%
On the other hand,
% TODO: Find a systematic tester that does this!
SKI \cite{ski}
is able to preempt threads around any shared resource access. Such fine granularity would automatically check if each data race is a real bug, but makes state space completion intractable for all but the most rudimentary test inputs.
%
This work shows how to avoid making this tradeoff decision in advance.

\newcommand\landslideid{\textsc{Landslide-ID}}
We present \landslideid...

@@

% TODO
TODO

@@

@@

Evaluation questions:
\begin{enumerate}
	\item Is ID more effective than 
\end{enumerate}

@@

% TODO: Mention dbug+PARROT as a motivating argument for our work. The number of tests with INF state space, EVEN WITH ONLY PTHREAD API PPs, shows that fixed-in-advance-pp-set needs our work to improve.

>>>>

% FIXME: decide whether "stateless model checking" or "sys testing"
\title{Systematic Testing with Data-Race Preemption Points}
\authorinfo{Ben Blum}{Carnegie Mellon University}{bblum@cs.cmu.edu}
\authorinfo{Garth Gibson}{Carnegie Mellon University}{garth@cs.cmu.edu}

@@

% Can I even make a claim this broad to begin with?
However, all stateless model checkers to date are bound by a fixed set of {\em preemption points} (PPs): code locations that define the granularity at which threads interleave.
For example, \textsc{CHESS} \cite{chess} preempts only on synchronization operations and library calls, which can miss lock-free shared memory races.
It provides an additional data-race analysis to report any violations of this model;
% TODO: Make sure that there are enough citations for this claim.
however, data-race analyses are prone to report false positives and benign races which require annotations or imprecise heuristics to reduce \cite{racerx,tsan,datacollider}.
%
On the other hand,
% TODO: Find a systematic tester that does this!
\textsc{Ski} \cite{ski}
is able to preempt threads around any shared resource access. Such fine granularity would automatically check if each data race is a real bug, but makes state space completion intractable for all but the most rudimentary test inputs.
%
This paper shows how to avoid making that tradeoff decision in advance.

\newcommand\landslideid{\textsc{Landslide-ID}}
We present \landslideid, a framework for {\em iterative deepening} (ID) of preemption points during stateless model checking.
Named after the analogous technique in chess AI \cite{iterative-deepening-chess},

This paper makes ELEVENTYBILLION contributions:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% TODO: Talk about the multiple ways DR PPs are added (alone / in addition)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Evaluation questions:
\begin{enumerate}
	\item Easy question: Is it good to incorporate DR analysis for new PPs? (Do we find DR-PP-only bugs?)
	\item How does this compare to static DR detection (how many DRs does ID verify as benign?)
	\item DRs aside, is ID more effective than the maximal state space? (Do we find bugs in subset spaces, when the max state space would time out?)
	\item Is ID useful for managing new DR PPs? (Are there some DRs where the PP alone finds the bug, and others where the old PP plus the new DR PP is needed?)
		% How many DR bugs were found from DR-alone state space, and how many from sema_foo + DR state space? What we want is a *variety*, which proves that iterative deepening is better than either individual strategy.
	\item How effective is the free-re-malloc technique at eliminating false positives? (Just turn the optimization off, and measure how many more SSes are generated.)

% Figure out concretely what the data race tricks are that we do, so we can claim them as contributions in the paper. Then ACTUALLY EVALUATE THEM.
%         - Speculative DR PPs.
%                 Not a heuristic, rather how to make it work at all to begin with.
%                 (Cite MS thesis, claim on backwards explorating finding bugs faster)
%         - Free/re-malloc to eliminate some false positives. See #193.
%                 Measure how many false positives are eliminated.
%                 Check, ofc, to make ABSOLUTE SURE, that no bugs missed w/ this trick.
%                         If there are, it could be because of the implementation
%                         bug described in #193.
%         - Using tid/last_call filtering because whole stack traces are too expensive.
%                 Turn on/off and measure how resulting DR bug #s change.
%         - Optional: Reprioritizing DRs based on "confirmed" / "suspected"
%                 Shouldn't be hard just make ID wrapper print "s" or "c"!
%                 Is it helpful for ID to put priorities on DR PPs?
%                         Test by inverting the priority and see if fewer buges are found.
%         // Super optional to talk about. Probably not worth the time.
%         // - "Too suspicious" (during init/destroy)
%         //      (Cite eraser, section 2.2)

\end{enumerate}

@@

% TODO: Mention dbug+PARROT as a motivating argument for our work. The number of tests with INF state space, EVEN WITH ONLY PTHREAD API PPs, shows that fixed-in-advance-pp-set needs our work to improve.
%Indeed, the low state space completion rate in dBug+Parrot's evaluation \cite{parrot} shows that for some tests even the set of all pthread API calls is too many PPs.

% TODO: Address ICB. Note that BPOR paper claims that ICB(3+) repeats LOADS of work, and that makes it ok for landslide-ID to repeat work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
